Validation of an Actuator Line Model Coupled to a Dynamic Stall Model for Pitching Motions Characteristic to Vertical Axis Turbines

### 2016-06-13 paper.tex
Take 'ALM' out of heading
Remove acronym from heading

\subsection{Actuator Line Model (ALM)}

@@

\subsection{Dynamic Stall Modeling (DSM)} The DSM is represented by the
Leishman-Beddoes model~\cite{leishman1986generalised} with the modifications of
Sheng et al.~\cite{sheng2008modified} and Dyachuk~\cite{dyachuk}. It is capable to
calculate the unsteady lift, pitching moment and drag, giving a physical
description of the aerodynamics. It have been validated with experimental data
in~\cite{leishman1989semi}. The model is separated into three subsystems: an
attached flow model for unsteady linear airloads, a separated flow model for
non-linear airloads and a dynamic stall model for the airloads induced by the
leading edge vortex.

>>>>

\subsection{Actuator Line Model}

@@

\subsection{Dynamic Stall Modeling}

The dynamic stall model (DSM) is represented by the Leishman-Beddoes
model~\cite{leishman1986generalised} with the modifications of Sheng et
al.~\cite{sheng2008modified} and Dyachuk~\cite{dyachuk}. It is capable to
calculate the unsteady lift, pitching moment and drag, giving a physical
description of the aerodynamics. It have been validated with experimental data
in~\cite{leishman1989semi}. The model is separated into three subsystems: an
attached flow model for unsteady linear airloads, a separated flow model for
non-linear airloads and a dynamic stall model for the airloads induced by the
leading edge vortex.
